Fuel switch, savings, electrification - Decarbonisation in industry OR Pathways to Carbon Neutral Industrial Sectors: Integrated Modelling Approach with High Level of Detail for End-use Processes OR Decarbonization options in industry and conceptual model of industry in the integrated energy system

### 2018-01-19 article.tex
geolocation part first draft finished

\\
This preliminary description of the Danish industry poses the bases for the modelling of the sector and the investigation of decarbonisation options. Indeed, with a clear overview of the end-use processes and the related fuel consumption, the industry sector can be conveniently integrated in an energy system model. 
The following section proposes a mathematical model for the industry sector and investigates on extensions to analyse decarbonisation options.

@@

\subsection{Geographical mapping of industrial energy consumption}
District heating plays a major role in Denmark. ... \% of of space heat demand is supplied via ... district heat networks. Provided that the supply of the district will be transformed to completely renewable ones \texit{(source Maries district heat paper?)}, an increased use of district heat for space and process heat for industry is an important option to reduce fossil fuel usage. The feasibility of this option depends on the location of this industrial demand. Whether the company is located within or in vicinity to a district heating area decides whether this option can be used. Depending on the required temperature, heat pumps would be necessary to raise the provided temperature. The vicinity to such a network is furthermore decisive for the possibility of excess heat usage. Connection to a district heat network offers the possibility to exploit the otherwise lost heat potential beyond recycling it on site.

@@

The basis this localalisation is the list of companies located in Denmark which includes addresses, affiliation to detailed industry group and number of employees information \cite{virk2017}. Entries that did not have any employees reduced the list from .... to .... The geographic location (coordinates) for the remaining were derived by matching the addresses to an address list containing coordinates \cite{}. This was done via a matching operation in python. \texit{State how much could not be located here?} District heat areas in Denmark are provided publicly from .... as a shapefile \cite{kortforsyningen2017} and were aggregated to the 36 areas as described in \cite{Petrovic2014} \textit{something to cite from Amalia?}. Via the coordinate information, the companies were assigned an area with a spatial join operation in the geographical software QGIS.

@@

@@

For electricity, the same approach is use for regions.

>>>>

This preliminary description of the Danish industry poses the bases for the modelling of the sector and the investigation of decarbonisation options. Indeed, with a clear overview of the end-use processes and the related fuel consumption, the industry sector can be conveniently integrated in an energy system model. 
The following section proposes a mathematical model for the industry sector and investigates on extensions to analyse decarbonisation options.

@@

\subsection{Geographical mapping of industrial energy consumption}
District heating plays a major role in Denmark. ... percent of of space heat demand is supplied via ... district heat networks. Provided that the supply of the district will be transformed to completely renewable ones \textit{(source Maries district heat paper?)}, an increased use of district heat for space and process heat for industry is an important option to reduce fossil fuel usage. The feasibility of this option depends on the location of this industrial demand. Whether the company is located within or in vicinity to a district heating area decides whether this option can be used. Depending on the required temperature, heat pumps would be necessary to raise the provided temperature. The vicinity to such a network is furthermore decisive for the possibility of excess heat usage. Connection to a district heat network offers the possibility to exploit the otherwise lost heat potential beyond recycling it on site.

@@

The basis this localalisation is the list of companies located in Denmark which includes addresses, affiliation to detailed industry group and number of employees information \cite{virk2017}. Entries that did not have any employees reduced the list from .... to .... The geographic location (coordinates) for the remaining were derived by matching the addresses to an address list containing coordinates \cite{}. This was done via a matching operation in python. \textit{State how much could not be located here?} District heat areas in Denmark are provided publicly from .... as a shapefile \cite{kortforsyningen2017} and were aggregated to the 36 areas as described in \cite{Petrovic2014} \textit{something to cite from Amalia?}. Via the coordinate information, the companies were assigned an area with a spatial join operation in the geographical software QGIS.

@@

Figure .... illustrates the progressing: Company locations mapped to Balmorel heat areas.

\includegraphics[scale=0.36]{img/DK_DH_Balmorel_areas2.png}
\caption District Heat Areas in Denmark. Sources: \cite{kortforsyningen2017,forsyningsomraade2017}}

\includegraphics[scale=0.36]{img/DK_DH_Balmorel_areas2_companies.png}
\caption{Location of Companies. Own processing based on: \cite{kortforsyningen2017,virk2017,aws2017,Buhler2017}}

One example of resulting data from the localisation is the share of space (Figure ...) and lower process heat (Figure ...) supplied already today by district heat for each Balmorel Area.

\includegraphics[scale=0.36]{img/DK_DH_Balmorel_areas2_DH_share_SH.png}
\caption{Space heat demand of companies supplied by district heat. Own calulations based on: \cite{kortforsyningen2017,virk2017,Buhler2017,Petrovic2014,VM2015,StatisticsDenmark2016}}

\includegraphics[scale=0.36]{img/DK_DH_Balmorel_areas2_DH_share_PHL.png}\\
\caption{Low process heat demand supplied by district heat. Own calulations based on: \cite{kortforsyningen2017,virk2017,Buhler2017,Petrovic2014,VM2015,StatisticsDenmark2016}}

@@

Yearly electricity demand and hourly profiles just have to be defined on a regional level. In the model, within Balmorel Regions, no transmission of electricity can be restricted within but just between regions. Thus, regions should be chosen in a way that bottlenecks that may occur within the scenario horizon are represented between regions. Following that rule, Denmark is modelled in two regions: Denmark East including Sealand and Denmark West including Jutland and Funen. Thus the same approach as described for heat in areas in applied in regions for localisation of electricity demand data.
